The pollination trade-off

### 2019-04-08 paper/manuscript.Rmd
Replace instances when "significant" is used to mean considerable
Prevent confusion with statistical significancy

We first examined the degree of facilitation/competition in natural communities. Specifically, we examined the slope of the relationship between the heterospecific and conspecific pollen deposited on stigmas of each species in a community. 
We found that overall neither facilitation nor competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
Indeed, we found that the proportion of species that experienced a significantly positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)). 
Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others. 
Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

@@

Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed. 
Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)). 
Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had significantly more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open (the difference was non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)). 
Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both significantly positive and negative differences.

@@

Overall, collinearity did not influence our findings qualitatively.
Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)). 
One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).

@@

All else being equal, our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
First, we found that the costs of pollinator sharing are pervasive. 
In particular, we found that a significant proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
Second, we found that multiple ecological factors can modulate the intensity of this competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these factors are likely to involve a trade-off between the quantity and quality of pollination. 
Third, we found that the way these factors influence competition is strongly shaped by the community context, this is, if collectively these factors are used to define a niche of competition for pollination, the same plant species can occupy dramatically different niches depending on the community it belongs to.

>>>>

We first examined the degree of facilitation/competition in natural communities. Specifically, we examined the slope of the relationship between the heterospecific and conspecific pollen deposited on stigmas of each species in a community. 
We found that overall neither facilitation nor competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
Indeed, we found that the proportion of species that experienced a statistically significant positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)). 
Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others. 
Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

@@

Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed. 
Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)). 
Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)). 
Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both positive and negative differences.

@@

Overall, collinearity did not affect our findings qualitatively.
Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)). 
One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).

@@

All else being equal, our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
First, we found that the costs of pollinator sharing are pervasive. 
In particular, we found that a considerable proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
Second, we found that multiple ecological factors can modulate the intensity of this competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these factors are likely to involve a trade-off between the quantity and quality of pollination. 
Third, we found that the way these factors influence competition is strongly shaped by the community context, this is, if collectively these factors are used to define a niche of competition for pollination, the same plant species can occupy dramatically different niches depending on the community it belongs to.
